\emph{Ab initio} Calculations of Intramolecular Exciton Transfer with Reduced Modes in Donor-Bridge-Acceptor Species

### 2016-04-25 Chapters/chap4/chap4.tex
Correct the size of images

%!TEX root = /Users/tcya/Dropbox/PhDthesis/thesis.tex
\chapter{Application on More Complex Molecules}\label{chap:chapt4}
\section{Introduction}

@@

\begin{figure*}[]
\includegraphics[width=0.45\columnwidth]{Chapters/chap4/Images/parabola.jpg}
\caption{Calculated energies of the CT (black), CSS (blue) and \textsuperscript{3}NAP (red) states along the NAP side C$\equiv$C coordinate in the ground state geometries of the molecules studied, in CH\textsubscript{2}Cl\textsubscript{2}. a, PTZ-CH\textsubscript{2}-Pt-NAP. b, PTZ-Pt-NAP. c, OMe-PTZ-Pt-NAP. The first and second vibrational energy levels for the asymmetric C$\equiv$C stretch are shown for the CT state. The energy gaps from $\nu_0$ to the intersection between CT and CSS are shown in the insets. There is a clear trend concerning the energy gap: PTZ-CH\textsubscript{2}-Pt-NAP < PTZ-Pt-NAP < OMe-PTZ-Pt-NAP, reflecting the trend experimentally observed in the efficiency of the infrared control effect. Reprinted with permission from Ref.~\cite{delor2015mechanism}.\label{PTZparabolas}} \end{figure*}

@@

\begin{figure}[]
\subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
\subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT13.png}}
% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT32.png}}
\caption{
Projection of primary mode of (a) CSS $\rightarrow$ \textsuperscript{3}NAP, (b) CT $\rightarrow$ \textsuperscript{3}NAP calculated at \textsuperscript{3}NAP geometry onto the normal modes of \textsuperscript{3}NAP. Embedded molecule shows the atomic displacement vectors of primary mode. If we focus on the C$\equiv$C bonds, PLMs are like
PTZ-Ph-C$\equiv$C-Pt-C$\protect\overset{\longleftrightarrow}{\equiv}$C-NAP
in (a) and
PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\longrightarrow}{C}\equiv\protect\overset{\longleftarrow}{C}$-NAP
in (b).}\label{projT1}
\end{figure}

\begin{figure}[]
% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT13.png}}
\subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
\subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT32.png}}
\caption{
Projection of primary mode of (a) CT $\rightarrow$ \textsuperscript{3}NAP, and (b) CT $\rightarrow$ CSS calculated at CT geometry onto the normal modes of CT. Embedded molecule shows the atomic displacement vectors of primary mode. If we focus on the C$\equiv$C bonds, PLMs are like
PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\rightarrow}{C}\equiv\protect\overset{\leftarrow}{C}$-NAP
in (a) and
PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\leftarrow}{C}\equiv\protect\overset{\rightarrow}{C}$-NAP
in (b).
}\label{projT3}
\end{figure}

>>>>

%!TEX root = /Users/tcya/Dropbox/XunmoYang/PhDthesis/thesis.tex
\chapter{Application on More Complex Molecules}\label{chap:chapt4}
\section{Introduction}

@@

\begin{figure*}[]
\includegraphics[width=0.44\columnwidth]{Chapters/chap4/Images/parabola.jpg}
\caption{Calculated energies of the CT (black), CSS (blue) and \textsuperscript{3}NAP (red) states along the NAP side C$\equiv$C coordinate in the ground state geometries of the molecules studied, in CH\textsubscript{2}Cl\textsubscript{2}. a, PTZ-CH\textsubscript{2}-Pt-NAP. b, PTZ-Pt-NAP. c, OMe-PTZ-Pt-NAP. The first and second vibrational energy levels for the asymmetric C$\equiv$C stretch are shown for the CT state. The energy gaps from $\nu_0$ to the intersection between CT and CSS are shown in the insets. There is a clear trend concerning the energy gap: PTZ-CH\textsubscript{2}-Pt-NAP < PTZ-Pt-NAP < OMe-PTZ-Pt-NAP, reflecting the trend experimentally observed in the efficiency of the infrared control effect. Reprinted with permission from Ref.~\cite{delor2015mechanism}.\label{PTZparabolas}} \end{figure*}

@@

\begin{figure}[]
\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT13.png}}
% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT32.png}}
\caption{
Projection of primary mode of (a) CSS $\rightarrow$ \textsuperscript{3}NAP, (b) CT $\rightarrow$ \textsuperscript{3}NAP calculated at \textsuperscript{3}NAP geometry onto the normal modes of \textsuperscript{3}NAP. Embedded molecule shows the atomic displacement vectors of primary mode. If we focus on the C$\equiv$C bonds, PLMs are like
PTZ-Ph-C$\equiv$C-Pt-C$\protect\overset{\longleftrightarrow}{\equiv}$C-NAP
in (a) and
PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\longrightarrow}{C}\equiv\protect\overset{\longleftarrow}{C}$-NAP
in (b).}\label{projT1}
\end{figure}

\begin{figure}[]
% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT13.png}}
\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT32.png}}
\caption{
Projection of primary mode of (a) CT $\rightarrow$ \textsuperscript{3}NAP, and (b) CT $\rightarrow$ CSS calculated at CT geometry onto the normal modes of CT. Embedded molecule shows the atomic displacement vectors of primary mode. If we focus on the C$\equiv$C bonds, PLMs are like
PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\rightarrow}{C}\equiv\protect\overset{\leftarrow}{C}$-NAP
in (a) and
PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\leftarrow}{C}\equiv\protect\overset{\rightarrow}{C}$-NAP
in (b).
}\label{projT3}
\end{figure}
